### 2019-06-10 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Proofreading

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall k \in [K]$, $\tau_k = 0$ and $n_k = 0$ \\
        \For{$t=1,2,\dots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in [K]$
            }{
                $A(t) = t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A(t) = \arg\max\limits_{k \in [K]} \mbox{UCB}_k(t)$ as defined in \eqref{def:6:UCB}
            }
            \mbox{Play arm } $A(t)$ \mbox{and receive the reward } $Y_{A(t),t}$ : $n_{A(t)} = n_{A(t)} + 1; Z_{A(t), n_{A(t)}} = Y_{A(t),t}$ \\
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A(t),1}, \dots, Z_{A(t), n_{A(t)}})$ = True
            }
            {
                \uIf{Global restart}{
                    $\forall k\in [K], \tau_k = t$ and $n_k = 0 $.
                    \tcp*[f]{global restart}
                    }
                \Else{
                    $\tau_{A(t)} = t$ and $n_{A(t)} = 0$
                    \tcp*[f]{local restart}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

@@

\paragraph{Other forced exploration schemes?}
%
We present in Appendix~\ref{sec:6:exploringDifferentForcedExplorationMechanisms} numerical simulations that compare three different options of forced exploration schemes.
We compare the uniformly random exploration used by \CUSUMUCB, against the deterministic scheme used in Algorithm~\ref{algo:6:GLRklUCB}, and against a more complicated scheme based on \emph{tracking}.
To sum-up these simulations, the deterministic scheme gives an efficient change-point detection algorithm, and an efficient \GLRklUCB{} policy.
As it is the simplest one to handle in our proofs, this is the one we chose for Algorithm~\ref{algo:6:GLRklUCB}.

@@

We highlight that \emph{this result is finite-time} and not asymptotic, even if it uses the notation $\bigO{\sqrt{\ln(T)}}$.
This last term does not mean the whole inequality is only valid for $T\to\infty$, but it rather means that at finite time, the inequality is valid with the last term being a function $g(T)$, which is upper-bounded by a constant times $\sqrt{\ln(T)}$ from a certain time $T_0$.

@@

\begin{corollary}\label{cor:6:Local}
\begin{leftbar}[corollarybar]  % XXX leftbar corollarybar, comment if needed
    For ``easy'' problems satisfying the corresponding Assumption~\ref{ass:6:LongPeriods},
    with $\Delta^{\text{opt}}$ and ${\Delta}^{\text{change}}$ defined as in Corollary~\ref{cor:6:Global}, the following holds.
    \begin{enumerate}
        \item Choosing $\alpha = \sqrt{\ln(T) / T}$, $\delta = 1 / \sqrt{T}$ gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2} \EffChange\sqrt{T\ln(T)} + \frac{1}{\left(\Delta^{\text{opt}}\right)^2} \EffChange\ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{\Upsilon_T\ln(T) / T}$, $\delta = 1 / \sqrt{\Upsilon_T T}$ gives
        \begin{equation}
            R_T = \bigO{\frac{K^2}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\Upsilon_T T\ln(T)} + \frac{K\Upsilon_T}{\left(\Delta^{\text{opt}}\right)^2}\ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{\EffChange\ln(T) / T}$, $\delta = 1 / \sqrt{\EffChange T}$ gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\EffChange T\ln(T)} + \frac{\EffChange}{\left(\Delta^{\text{opt}}\right)^2}\ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{K\Upsilon_T\ln(T) / T}$, $\delta = 1 / \sqrt{K\Upsilon_T T}$ gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\EffChange T\ln(T)} + \frac{1}{\left(\Delta^{\text{opt}}\right)^2} \EffChange\ln(T)}.
        \end{equation}
    \end{enumerate}
\end{leftbar}  % XXX leftbar corollarybar, comment if needed
\end{corollary}

@@

\begin{align*}
    (A) & \leq \bE\left[\indic(\cE_T) \sum_{t=1}^T \indic\left(n_{k_t^*}(t) \, \kl\left(\widehat{\mu}_{k_t^*}(t), \mu_{k_t^*}(t)\right) \geq f(t - \tau(t))\right)\right] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\left[\indic(\cE_T) \sum_{t=\tau^{(i)}+1}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}(t))\right)\right] \\
    & \leq \sum_{k=1}^{\Upsilon_T}\bE\left[ d^{(i)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right)\right] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d^{(i)} + \sum_{k=1}^{\Upsilon_T}\bE\left[\indic(\cC^{(i)}) \sum_{t=wide\hat{\tau}^{(i)}}^{\tau^{(i+1)}}\indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}\right) \geq f(t - \widehat{\tau}^{(i)})\right)\right],
\end{align*}
%
where we introduce the event $\cC^{(i)}$ that all the changes up to the $k$-th have been detected:
%
\begin{equation}\label{def:6:EventCiGlobal}
    \cC^{(i)} = \left\{\forall j \leq k, \widehat{\tau}^{(j)} \in \{\tau^{(j)} + 1, \dots, \tau^{(j)} + d^{(j)} \} \right\}.
\end{equation}
%
Clearly, $\cE_T \subseteq \cC^{(i)}$ and $\cC^{(i)}$ is $\cF_{\widehat{\tau}^{(i)}}$-measurable. Observe that conditionally to $\cF_{\widehat{\tau}^{(i)}}$, when $\cC^{(i)}$ holds, $\widehat{\mu}_{k^*}(t)$ is the average of samples that have all mean $\mu_{k^*}^{(i)}$.
%
Thus, introducing $\widehat{\mu}_s$ as a sequence of \iid{} random variables with mean $\mu_{k^*}^{(i)}$, one can write
%
\begin{align*}
    &\bE\left[\left.\indic(\cC^{(i)}) \sum_{t=wide\hat{\tau}^{(i)}}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right) \right| \cF_{\widehat{\tau}^{(i)}}\right]\\
    & = \indic(\cC^{(i)}) \sum_{t=\widehat{\tau}^{(i)}}^{\tau^{(i+1)}} \bE\left[\indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right) \;|\; \cF_{\widehat{\tau}^{(i)}}\right] \\
    & \leq \indic(\cC^{(i)}) \sum_{t'=1}^{\tau^{(i+1)} - \widehat{\tau}^{(i)}} \bP\left(\exists s \leq t' : s \, \kl(\widehat{\mu}_{s},\mu_{k^*}^{(i)}) \geq f(t')\right) \\
    & \leq \sum_{t=1}^T \frac{1}{t\ln(t)} \leq \ln(\ln(T)),
\end{align*}
%
where the last but one inequality relies on the concentration inequality given in Lemma~2 of \cite{KLUCBJournal} and the choice $f(t) = \ln(t) + 3 \ln(\ln(t))$.
Finally, using the law of total expectation yields
\begin{equation}\label{eq:6:TermAFinalGlobal}
    (A) \leq \sum_{k=1}^{\Upsilon_T}\left[d^{(i)} + \ln(\ln(T))\right].
\end{equation}

\paragraph{Upper bound on term $(B)$.}
%
We let $\widetilde{\mu}_{k,s}^{(i)}$ denote the empirical mean of the first $s$ observations of arm $k$ made after time $t=\widehat{\tau}^{(i)}+1$.
Rewriting the sum in $t$ as the sum of consecutive intervals $[\tau^{(i)}+1, \tau^{(i+1)}]$, we obtain
%
\begin{align*}
    (B) & \leq \bE\Big[\indic(\cE_T)\sum_{k=1}^{\Upsilon_T} \sum_{t=\tau^{(i)}}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_{A(t)}^{(i)}\right)\indic\left(\UCB_{A(t)}(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\Big[\indic(\cE_T)\widehat{\tau}^{(i)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_{A(t)}^{(i)}\right)\indic\left(\UCB_{A(t)}(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \bE\Big[\indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\indic\left(A(t)=i,\UCB_k(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\times \\
    &\hspace{1cm}\bE\Big[\indic(\cE_T) \sum_{t=wide\hat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\sum_{s=1}^{t-\widehat{\tau}^{(i)}}\indic\left(A(t) = i,n_k(t) = s\right) \indic\left(s \, \kl(\widetilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \widehat{\tau}^{(i)})\right)\Big]
\end{align*}%
\begin{align*}
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\bE\Big[\indic(\cE_T) \sum_{s=1}^{n_k(\tau^{(i+1)})}\indic\left(s \, \kl(wide\tilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \tau^{(i)})\right)\Big]  \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\bE\Big[\indic(\cC^{(i)}) \sum_{s=1}^{n_k(\tau^{(i+1)})}\indic\left(s \, \kl(\widetilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \tau^{(i)})\right)\Big].
\end{align*}

@@

First, it follows from Proposition~\ref{prop:6:EnoughSamples} that there exists $\overline{t} \in \{\tau^{(i)}, \dots, \tau^{(i)} + d^{(i)} \}$ such that
$n_k(\overline{t}) - n_k(\tau^{(i)}) = \overline{r}$ where $\overline{r} = \lfloor \frac{\alpha}{K} d^{(i)}\rfloor$
(as the mapping $t\mapsto n_k(t) - n_k(\tau^{(i)})$ is non-decreasing, is $0$ at $t=\tau^{(i)}$ and its value at $\tau^{(i)}+d^{(i)}$ is larger than $\overline{r}$).
Using that $\left(\widehat{\tau}^{(i)} \geq \tau^{(i)} + d^{(i)}\right) \subseteq \left(\widehat{\tau}^{(i)} \geq \overline{t}\right)$
the event $\left(\widehat{\tau}^{(i)} \geq \tau^{(i)} + d^{(i)}\right)$ further implies that
\[
    n_k(\tau^{(i)}) \, \kl\left(\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)})},\widetilde{\mu}^{k-1}_{i,n_k(\overline{t})}\right)
    + \overline{r} \, \kl\left(\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)}) : n_k(\overline{t})},\widetilde{\mu}^{k-1}_{i,n_k(\overline{t})}\right) \leq \beta(n_k(\tau^{(i)}) + \overline{r},\delta),
\]
where $\widetilde{\mu}^{k-1}_{k,s}$ denotes the empirical mean of the $s$ first observation of arm $k$ since the $(k-1)$-th restart $\widehat{\tau}^{(i-1)}$ and  $wide\tilde{\mu}^{k-1}_{i,s:s'}$ the empirical mean that includes observation number $s$ to number $s'$. Conditionally to $\cC^{(i-1)}$, $\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)})}$ is the empirical mean of $n_k(\tau^{(i)})$ \iid{} replications of mean $\mu^{k-1}$, whereas $\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)}) : n_k(\overline{t})}$ is the empirical mean of $\overline{r}$ \iid{} replications of mean $\mu_k^{k}$.

>>>>

\TODOL{Si on veut, on peut déplacer cette preuve en Annexe, voir même l'enlever, elle n'est pas spécialement palpitante et pas requise pour la suite !}

@@

\begin{figure}[h!]
    \centering
    \begin{framed}
    % \begin{small}
    % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
    % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
    % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
    \begin{algorithm}[H]
        % XXX Options
        % \LinesNumbered  % XXX Option to number the line
        % \RestyleAlgo{boxed}
        % XXX Input, data and output
        % \KwIn{\emph{Problem parameters}: $T\in\N^*$, $K\in\N^*$\;}
        \KwIn{\emph{Parameters}: exploration probability $\alpha \in (0, 1)$, confidence level $\delta>0$\;}
        \KwIn{\emph{Option}: \textbf{Local} or \textbf{Global} restart\;}
        % \KwData{Data}
        % \KwResult{Result}
        % XXX Algorithm
        \textbf{Initialization: } $\forall k \in [K]$, $\tau_k = 0$ and $n_k = 0$ \\
        \For{$t=1,2,\dots, T$}{
            \uIf{
                $\alpha>0$ and $t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor \in [K]$
            }{
                $A(t) = t \mod \left\lfloor \frac{K}{\alpha}\right\rfloor$
                \tcp*[f]{forced exploration} \\
            }
            \Else{
                $A(t) = \arg\max\limits_{k \in [K]} \mbox{UCB}_k(t)$ as defined in \eqref{def:6:UCB}
            }
            \mbox{Play arm } $A(t)$ \mbox{and receive the reward } $Y_{A(t),t}$ : $n_{A(t)} = n_{A(t)} + 1; Z_{A(t), n_{A(t)}} = Y_{A(t),t}$ \\
            \uIf(\tcp*[f]{Change point is detected}){
                $\GLR_\delta(Z_{A(t),1}, \dots, Z_{A(t), n_{A(t)}})$ = True
            }
            {
                \uIf{Global restart}{
                    $\forall k\in [K], \tau_k = t$ and $n_k = 0 $.
                    \tcp*[f]{global restart}
                    }
                \Else{
                    $\tau_{A(t)} = t$ and $n_{A(t)} = 0$
                    \tcp*[f]{local restart}
                }
            }
        }
        \caption{\GLRklUCB, with \textbf{Local} or \textbf{Global} restarts}
        \label{algo:6:GLRklUCB}
    \end{algorithm}
    % \end{small}
    \end{framed}
\end{figure}

@@

\textbf{Other forced exploration schemes?}
%
We present in Appendix~\ref{sec:6:exploringDifferentForcedExplorationMechanisms} numerical simulations that compare three different options of forced exploration schemes.
We compare the uniformly random exploration used by \CUSUMUCB, against the deterministic scheme used in Algorithm~\ref{algo:6:GLRklUCB}, and against a more complicated scheme based on \emph{tracking}.
To sum-up these simulations, the deterministic scheme gives an efficient change-point detection algorithm, and an efficient \GLRklUCB{} policy.
As it is the simplest one to handle in our proofs, this is the one we chose for Algorithm~\ref{algo:6:GLRklUCB}.

@@

\textbf{\textcolor{red}{Warning}:}
%
We highlight that \emph{this result is finite-time} and not asymptotic, even if it uses the notation $\bigO{\sqrt{\ln(T)}}$.
This last term does not mean the whole inequality is only valid for $T\to\infty$, but it rather means that at finite time, the inequality is valid with the last term being a function $g(T)$, which is upper-bounded by a constant times $\sqrt{\ln(T)}$ from a certain time $T_0$.

@@

\begin{corollary}\label{cor:6:Local}
\begin{leftbar}[corollarybar]  % XXX leftbar corollarybar, comment if needed
    For ``easy'' problems satisfying the corresponding Assumption~\ref{ass:6:LongPeriods},
    with $\Delta^{\text{opt}}$ and ${\Delta}^{\text{change}}$ defined as in Corollary~\ref{cor:6:Global}, the following regret bounds hold.
    \begin{enumerate}
        \item Choosing $\alpha = \sqrt{\ln(T) / T}$, $\delta = 1 / \sqrt{T}$ (with no prior knowledge of $\Upsilon_T$ or $\EffChange$) gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left(\Delta^{\text{change}}\right)^2} \textcolor{red}{\EffChange}\sqrt{T\ln(T)} + \frac{\EffChange}{\left(\Delta^{\text{opt}}\right)^2} \ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{\Upsilon_T\ln(T) / T}$, $\delta = 1 / \sqrt{\Upsilon_T T}$ (with prior knowledge of $\Upsilon_T$ and optimist guess $\Upsilon_T \simeq \EffChange \ll K \Upsilon_T$) gives
        \begin{equation}
            R_T = \bigO{\frac{K^{\textcolor{red}{2}}}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\Upsilon_T T\ln(T)} + \frac{K\Upsilon_T}{\left(\Delta^{\text{opt}}\right)^2}\ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{\EffChange\ln(T) / T}$, $\delta = 1 / \sqrt{\EffChange T}$ (with prior knowledge of $\EffChange$) gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\EffChange T\ln(T)} + \frac{\EffChange}{\left(\Delta^{\text{opt}}\right)^2}\ln(T)},
        \end{equation}
        \item Choosing $\alpha = \sqrt{K\Upsilon_T\ln(T) / T}$, $\delta = 1 / \sqrt{K\Upsilon_T T}$ (with prior knowledge of $\Upsilon_T$ and pessimist guess $\EffChange \simeq K \Upsilon_T$) gives
        \begin{equation}
            R_T = \bigO{\frac{K}{\left({\Delta}^{\text{change}}\right)^2}\sqrt{\EffChange T\ln(T)} + \frac{\EffChange}{\left(\Delta^{\text{opt}}\right)^2} \ln(T)}.
        \end{equation}
    \end{enumerate}
\end{leftbar}  % XXX leftbar corollarybar, comment if needed
\end{corollary}

@@

\begin{align*}
    (A) & \leq \bE\left[\indic(\cE_T) \sum_{t=1}^T \indic\left(n_{k_t^*}(t) \, \kl\left(\widehat{\mu}_{k_t^*}(t), \mu_{k_t^*}(t)\right) \geq f(t - \tau(t))\right)\right] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\left[\indic(\cE_T) \sum_{t=\tau^{(i)}+1}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}(t))\right)\right] \\
    & \leq \sum_{k=1}^{\Upsilon_T}\bE\left[ d^{(i)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right)\right] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d^{(i)} + \sum_{k=1}^{\Upsilon_T}\bE\left[\indic(\cC^{(i)}) \sum_{t=\widehat{\tau}^{(i)}}^{\tau^{(i+1)}}\indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}\right) \geq f(t - \widehat{\tau}^{(i)})\right)\right],
\end{align*}
%
where we introduce the event $\cC^{(i)}$ that all the changes up to the $k$-th have been detected:
%
\begin{equation}\label{def:6:EventCiGlobal}
    \cC^{(i)} = \left\{\forall j \leq k, \widehat{\tau}^{(j)} \in \{\tau^{(j)} + 1, \dots, \tau^{(j)} + d^{(j)} \} \right\}.
\end{equation}
%
Clearly, $\cE_T \subseteq \cC^{(i)}$ and $\cC^{(i)}$ is $\cF_{\widehat{\tau}^{(i)}}$-measurable. Observe that conditionally to $\cF_{\widehat{\tau}^{(i)}}$, when $\cC^{(i)}$ holds, $\widehat{\mu}_{k^*}(t)$ is the average of samples that have all mean $\mu_{k^*}^{(i)}$.
%
Thus, introducing $\widehat{\mu}_s$ as a sequence of \iid{} random variables with mean $\mu_{k^*}^{(i)}$, one can write
%
\begin{align*}
    &\bE\left[\left.\indic(\cC^{(i)}) \sum_{t=\widehat{\tau}^{(i)}}^{\tau^{(i+1)}} \indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right) \right| \cF_{\widehat{\tau}^{(i)}}\right]\\
    & = \indic(\cC^{(i)}) \sum_{t=\widehat{\tau}^{(i)}}^{\tau^{(i+1)}} \bE\left[\indic\left(n_{k^*}(t) \, \kl\left(\widehat{\mu}_{k^*}(t), \mu_{k^*}^{(i)}\right) \geq f(t - \widehat{\tau}^{(i)})\right) \;|\; \cF_{\widehat{\tau}^{(i)}}\right] \\
    & \leq \indic(\cC^{(i)}) \sum_{t'=1}^{\tau^{(i+1)} - \widehat{\tau}^{(i)}} \bP\left(\exists s \leq t' : s \, \kl(\widehat{\mu}_{s},\mu_{k^*}^{(i)}) \geq f(t')\right) \\
    & \leq \sum_{t=1}^T \frac{1}{t\ln(t)} \leq \ln(\ln(T)),
\end{align*}
%
where the last but one inequality relies on the concentration inequality given in Lemma~2 of \cite{KLUCBJournal} and the choice $f(t) = \ln(t) + 3 \ln(\ln(t))$.
Finally, using the law of total expectation yields
\begin{equation}\label{eq:6:TermAFinalGlobal}
    (A) \leq \sum_{k=1}^{\Upsilon_T}\left[d^{(i)} + \ln(\ln(T))\right].
\end{equation}

\paragraph{Upper bound on term $(B)$.}
%
We let $\widetilde{\mu}_{k,s}^{(i)}$ denote the empirical mean of the first $s$ observations of arm $k$ made after time $t=\widehat{\tau}^{(i)}+1$.
Rewriting the sum in $t$ as the sum of consecutive intervals $[\tau^{(i)}+1, \tau^{(i+1)}]$, we obtain
%
\begin{align*}
    (B) & \leq \bE\Big[\indic(\cE_T)\sum_{k=1}^{\Upsilon_T} \sum_{t=\tau^{(i)}}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_{A(t)}^{(i)}\right)\indic\left(\UCB_{A(t)}(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
     & \leq \sum_{k=1}^{\Upsilon_T}\bE\Big[\indic(\cE_T)\widehat{\tau}^{(i)} + \indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_{A(t)}^{(i)}\right)\indic\left(\UCB_{A(t)}(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \bE\Big[\indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\indic\left(A(t)=i,\UCB_k(t) \geq \mu_{k^*}^{(i)}\right)\Big] \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\times \\
    &\hspace{1cm}\bE\Big[\indic(\cE_T) \sum_{t=\widehat{\tau}^{(i)}+1}^{\tau^{(i+1)}}\sum_{s=1}^{t-\widehat{\tau}^{(i)}}\indic\left(A(t) = i,n_k(t) = s\right) \indic\left(s \, \kl(\widetilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \widehat{\tau}^{(i)})\right)\Big]
% \end{align*}%
% \begin{align*}
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\bE\Big[\indic(\cE_T) \sum_{s=1}^{n_k(\tau^{(i+1)})}\indic\left(s \, \kl(\widetilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \tau^{(i)})\right)\Big]  \\
    & \leq \sum_{k=1}^{\Upsilon_T}d_k^{(i)}+ \sum_{k=1}^K \sum_{k=1}^{\Upsilon_T}\left(\mu_{k^*}^{(i)} - \mu_k^{(i)}\right)\bE\Big[\indic(\cC^{(i)}) \sum_{s=1}^{n_k(\tau^{(i+1)})}\indic\left(s \, \kl(\widetilde{\mu}_{k,s}^{(i)}, \mu_{k^*}^{(i)}) \leq f(\tau^{(i+1)} - \tau^{(i)})\right)\Big].
\end{align*}

@@

First, it follows from Proposition~\ref{prop:6:EnoughSamples} that there exists $\overline{t} \in \{\tau^{(i)}, \dots, \tau^{(i)} + d^{(i)} \}$ such that
$n_k(\overline{t}) - n_k(\tau^{(i)}) = \overline{r}$ where $\overline{r} = \lfloor \frac{\alpha}{K} d^{(i)}\rfloor$
(as the mapping $t\mapsto n_k(t) - n_k(\tau^{(i)})$ is non-decreasing, is $0$ at $t=\tau^{(i)}$ and its value at $\tau^{(i)}+d^{(i)}$ is larger than $\overline{r}$).
Using that $\left(\widehat{\tau}^{(i)} \geq \tau^{(i)} + d^{(i)}\right) \subseteq \left(\widehat{\tau}^{(i)} \geq \overline{t}\right)$
the event $\left(\widehat{\tau}^{(i)} \geq \tau^{(i)} + d^{(i)}\right)$ further implies that
\[
    n_k(\tau^{(i)}) \, \kl\left(\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)})},\widetilde{\mu}^{k-1}_{i,n_k(\overline{t})}\right)
    + \overline{r} \, \kl\left(\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)}) : n_k(\overline{t})},\widetilde{\mu}^{k-1}_{i,n_k(\overline{t})}\right) \leq \beta(n_k(\tau^{(i)}) + \overline{r},\delta),
\]
where $\widetilde{\mu}^{k-1}_{k,s}$ denotes the empirical mean of the $s$ first observation of arm $k$ since the $(k-1)$-th restart $\widehat{\tau}^{(i-1)}$ and  $\widetilde{\mu}^{k-1}_{i,s:s'}$ the empirical mean that includes observation number $s$ to number $s'$. Conditionally to $\cC^{(i-1)}$, $\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)})}$ is the empirical mean of $n_k(\tau^{(i)})$ \iid{} replications of mean $\mu^{k-1}$, whereas $\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)}) : n_k(\overline{t})}$ is the empirical mean of $\overline{r}$ \iid{} replications of mean $\mu_k^{k}$.

Moreover, due to Proposition~\ref{prop:6:EnoughSamples}, $n_k(\tau^{(i)})$ lies in the interval $
\left[\left\lfloor \frac{\alpha}{K}\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right\rfloor,\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right]$.
Conditionally to $\cC^{(i-1)}$,
by using Assumption~\ref{ass:6:LongPeriodsGlobal},
we can prove that $d^{(i-1)} \leq (\tau^{(i)} - \tau^{(i-1)})/2$,
and thus we obtain furthermore that
%
\begin{equation*}
    n_k(\tau^{(i)}) \in \left\{ \left\lfloor \frac{\alpha}{2K} (\tau^{(i)}-\tau^{(i-1)} )\right\rfloor, \dots, \tau^{(i)}-\tau^{(i-1)} \right\} \eqdef \cI_k.
\end{equation*}
%
Introducing $\widehat{\mu}_{a,s}$ (resp. $\widehat{\mu}_{b,s}$) the empirical mean of $s$ \iid{} observations with mean $\widehat{\mu}_k^{(i-1)}$ (resp. $\widehat{\mu}_k^{(i)}$), such that $\widehat{\mu}_{a,s}$ and $\widehat{\mu}_{b,r}$ are independent, it follows that
\[
    (b)  \leq \bP\left(\exists s \in \cI_k : s \, \kl\left(\widehat{\mu}_{a,s},\frac{s\widehat{\mu}_{a,s}+\overline{r}\widehat{\mu}_{b,\overline{r}}}{s+\overline{r}} \right) +  \overline{r} \, \kl\left(\widehat{\mu}_{b,\overline{r}},\frac{s\widehat{\mu}_{a,s}+\overline{r}\widehat{\mu}_{b,\overline{r}}}{s+\overline{r}}  \right)  \leq \beta(s+\overline{r},\delta)\right),
\]
where we have also used that $\widetilde{\mu}^{k-1}_{i,n_k(\overline{t})} = \left(n_k(\tau^{(i)})\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)})} + \overline{r}\widetilde{\mu}^{k-1}_{i,n_k(\tau^{(i)}) : n_k(\overline{t})} \right) / (n_k(\tau^{(i)}) + \overline{r})$.
